---
title: "Exploring Palmer Penguins with R"
author: "Yunpeng Xie"
date: 2026-09-25
---

## Introduction

In this post, I explore the Palmer Penguins dataset using R. The dataset contains measurements for penguins from three species observed in the Palmer Archipelago, Antarctica.

Data source: [Palmer Penguins](https://allisonhorst.github.io/palmerpenguins/)

## Load the data

```{r}
library(palmerpenguins)
library(dplyr)
library(ggplot2)

penguins <- palmerpenguins::penguins
head(penguins)
```

## Summary by species

The following table compares the average body mass and flipper length across the three penguin species.

```{r}
species_summary <- penguins |>
  group_by(species) |>
  summarise(
    mean_body_mass_g = mean(body_mass_g, na.rm = TRUE),
    mean_flipper_length_mm = mean(flipper_length_mm, na.rm = TRUE)
  )

species_summary
```

## Flipper length and body mass

The scatter plot below shows the relationship between flipper length and body mass for each penguin species.

```{r}
ggplot(
  penguins,
  aes(
    x = flipper_length_mm,
    y = body_mass_g,
    color = species
  )
) +
  geom_point(alpha = 0.7) +
  labs(
    title = "Body mass vs. flipper length by species",
    x = "Flipper length (mm)",
    y = "Body mass (g)",
    color = "Species"
  ) +
  theme_minimal()
```